### 2019-06-08 2-Chapters/5-Chapter/chapter5.tex
Almost done for ch5
Done for ch5

As reminded above, the model assumes that the number of players $M$ remains fixed during all the bandit game.
However, in real-world wireless networks, when players model communicating devices connected to a single gateway, devices can arrive or leave the network at any time.
The existing previous work on multi-player bandit models are all motivated by possible applications to wireless networks, but most of them assume $M$ to be fixed.
The first work studying the relaxation of this hypothesis is \cite{Rosenski16}, where this case is called the ``dynamic setting''.
If the arrival or departures of players is not random, but determined in advance while still being unknown to any player, the natural notion of regret is the following, where the expectancy $\E[\bullet]$ is capturing the randomness in the sensing information, as well as in the players' decisions (\ie, collisions):
\begin{equation}\label{eq:5:defRegretDynamicSetting}
    R_T^{\text{dyn}} = \sum_{t=1}^T \sum_{k=1}^{M(t)} \mu^*_{k} - \E\Bigl[ \sum_{t=1}^T \sum_{j=1}^{M(t)} r^j(t) \Bigr].
\end{equation}

@@

In \cite{darak2016bayesian,Darak16}, the authors study the same model and focussed on the \RhoRand{} policy, which was the state-of-the-art back in $2016$, combined with \UCB{} or \klUCB, as well as an extension using Bayes-UCB from \cite{Kaufmann12BUCB}.
Their idea is to use the same skeleton as \RhoRand, that is to assign a \emph{rank} to each player, and make players change their rank after any collision. But instead of selecting a new rank uniformly at random among $[M]$, they proposed to use a ``second-stage'' learning policy\footnote{This is a very natural idea: use a bandit algorithm to balance the exploration/exploitation aspect of rank selection, instead of a random hoping.}, based on Bayes-UCB, to (try to) learn the best rank while still exploring each rank from time to time.
This algorithm is implemented in SMPyBandits and named \rhoLearn,
% \footnote{See \href{https://smpybandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}{\texttt{SMPyBandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}} for its documentation.},
where it can use Bayes-UCB or any of the $65$ or more bandit algorithms available in the library.
Even if no theoretical guarantee backs up this idea of second-stage learning with Bayes-UCB, empirical simulations found that it can be efficient.
We illustrate this in Table~\ref{table:5:comparisonRhoRandRhoLearn} below, where we consider the same problem as described above in Section~\ref{sub:5:withoutSensing} (Table~\ref{table:5:meanRegretSimulationsNoSensing}).
The first \rhoLearn uses \klUCB{}, Bayes-UCB or Exp3 for the second-stage learning,
and we include both the centralized multiple-play version of \klUCB{} and \MCTopM-\klUCB{} for comparison.

>>>>

As reminded above, the model assumes that the number of players $M$ remains fixed during all the bandit game.
However, in real-world wireless networks, when players model communicating devices connected to a single gateway, devices can arrive or leave the network at any time.
The existing previous work on multi-player bandit models are all motivated by possible applications to wireless networks, but most of them assume $M$ to be fixed.
The first work studying the relaxation of this hypothesis is \cite{Rosenski16}, where this case is called the ``dynamic setting''.
If the arrival or departures of players is not random, but determined in advance while still being unknown to any player, the natural notion of regret is the following, where the expectancy $\E[\bullet]$ is capturing the randomness in the sensing information, as well as in the players' decisions (\ie, collisions):
\begin{equation}\label{eq:5:defRegretDynamicSetting}
    R_T^{\text{dyn}} := \sum_{t=1}^T \sum_{k=1}^{M(t)} \mu^*_{k} - \E\Bigl[ \sum_{t=1}^T \sum_{j=1}^{M(t)} r^j(t) \Bigr].
\end{equation}

@@

In \cite{darak2016bayesian,Darak16}, the authors study the same model and focussed on the \RhoRand{} policy, which was the state-of-the-art back in $2016$, combined with \UCB{} or \klUCB, as well as an extension using Bayes-UCB from \cite{Kaufmann12BUCB}.
Their idea is to use the same skeleton as \RhoRand, that is to assign a \emph{rank} to each player, and make players change their rank after any collision. But instead of selecting a new rank uniformly at random among $[M]$, they proposed to use a ``second-stage'' learning policy\footnote{This is a very natural idea: use a bandit algorithm to balance the exploration/exploitation aspect of rank selection, instead of a random hoping.}, based on Bayes-UCB, to (try to) learn the best rank while still exploring each rank from time to time.
This algorithm is implemented in SMPyBandits and named \rhoLearn,
% \footnote{See \href{https://smpybandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}{\texttt{SMPyBandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}} for its documentation.},
where it can use Bayes-UCB or any of the $65$ or more bandit algorithms available in the library.
Even if no theoretical guarantee backs up this idea of second-stage learning with Bayes-UCB, empirical simulations found that it can be efficient.
We illustrate this in Table~\ref{table:5:comparisonRhoRandRhoLearn} below, where we consider the same problem as described above in Section~\ref{sub:5:withoutSensing} (Table~\ref{table:5:meanRegretSimulationsNoSensing}).
We include different \rhoLearn{} algorithms, that uses \klUCB{}, Bayes-UCB or Exp3 for the second-stage learning,
and we include both the centralized multiple-play version of \klUCB{} and \MCTopM-\klUCB{} for comparison.
